Meta-analysis

### 2020-07-09 04_MetaAnalysis.Rmd
Completed forest plot showing the variation of mean grain differences in each trial

Lets look at the trial variability in this model with a forest plot
```{r forestP, fig.height= 25, fig.width=20}
change_labels <- function(x1) {
   x1 <- gsub(pattern = "spray_management",
              replacement = "",
              x = x1)
   x1
}

polys <- data.frame(ref = change_labels(names(coef(PM_mv))),
                    x = coef(PM_mv),
                    ci.lb = PM_mv$ci.lb,
                    ci.ub = PM_mv$ci.ub,
                    rows = c(120.60, 68.6, 24.6,99.6, 1.6))

metafor::forest(PM_mv, cex = 1.15 , width = 5,
                order = "fit",
                rows = c(134:122, 117:101, 96:70, 65:26, 21:3),
                ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, 
                             dat1$row_spacing, dat1$host_genotype, dat1$dose),
                ilab.xpos = c(-3.3, -2.85,-2.55,-2.35,-2.15,-1.85),
                slab = NA, 
                xlim = c(-3.5, 2.5),
                ylim = c(4,137),
                xlab = "Grain yield mean difference",
                addfit = FALSE,
                efac = c(0.5,2,0.2))

### add text with Q-value, dfs, p-value, and I^2 statistic
text(-5.1, -0.8, pos=3, cex=0.75, bquote(paste("RE Model for All Studies (Q = ",
     .(formatC(PM_mv$QE, digits=2, format="f")), ", df = ", .(PM_mv$k - PM_mv$p),
     ", p = ", .(formatC(PM_mv$QEp, digits=3, format="f")), ") ")))

### add column headings to the plot
text(c(-3.3, -2.85,-2.55,-2.35,-2.15,-1.85, -1.5), 137.9,cex = 1, 
     c("Trial\nReference", "Location", "Year", "Row\nSpacing","Host\nCultivar","DMI dose"),
     font = 2)

text(-2.35, polys$rows ,cex = 1.3, 
     paste0(polys$ref," Spray Schedule - (tau^2 = " ,round(PM_mv$tau2, digits = 3), ") "),
     font = 2)

addpoly(x = polys$x,
        ci.lb = polys$ci.lb,
        ci.ub = polys$ci.ub,
        col ="black",
        rows = polys$rows,
        cex = 1.3,
        efac = 0.2,
        font = "Arial Rounded MT Bold")

>>>>

Lets look at the trial variability in this model with a forest plot
```{r forestP, fig.height= 40, fig.width=17}
source(here("R/change_labels.R"))
source(here("R/forest_rows.R"))

### Sort and arrange data-frame occordingly and produce a index vector to inform the order of each "Trial" on the plot
index1 <- dat1 %>%
   mutate(ID = seq_along(trial_ref)) %>%
   mutate(spray_management = 
             factor(spray_management, 
                    levels = c("Early","Late","Recommended",
                    "Recommended_plus","Late_plus"))) %>%
   arrange(desc(spray_management), location, desc(grain_MD)) %>%
   mutate(ID2 = order(ID))%>%
   pull(ID2)

### Use forest rows function to return a list of where to place on the plot: sub-titles, each trial row, and summary prediction for each treatment.
### this list can be used below to reference where to plot each variable
rows1 <- forest_rows(head_row = 156, 
                     ord_var = dat1$spray_management, 
                     index = index1, 
                     gap = 5, 
                     row_offset = -2)

### A data-frame of meta-model coefficients used to produce the summary polygons for each treatment
polys <- data.frame(ref = change_labels(names(coef(PM_mv))),
                    x = coef(PM_mv),
                    ci.lb = PM_mv$ci.lb,
                    ci.ub = PM_mv$ci.ub)[c(1,4,2,3,5),]
polys$rows <- rows1$pred_row - 1.5

forest1  <- metafor::forest(PM_mv, cex = 1.15 , width = 5,
                #order = "fit",
                rows = rows1$trows-1.5,
                ilab = cbind(dat1$year, 
                             dat1$row_spacing, dat1$host_genotype, dat1$dose),
                ilab.xpos = c(-2.35,-2.1,-1.8,-1.4),
                slab = NA, 
                xlim = c(-2.9, 2.2),
                ylim = c(18,157),
                xlab = "Grain yield mean difference",
                addfit = FALSE,
                efac = c(0.2,0.15,0.2),
                at = seq(-1,1.5, 0.5))

### code which puts lines and annotations on the plot, its a bit long...
source(here("R/add_annotations.R"))
